---
title: "Daniel Vartanian's Résumé"
author: Daniel Vartanian
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: false
output:
  pagedown::html_resume:
    css: ["resume", "css/dd_cv.css", "css/custom.css"]
    self_contained: true
---

<!-- See <https://pagedown.rbind.io/#resume> to learn more. -->

```{r, include=FALSE}
knitr::opts_chunk$set(
  results = "asis",
  echo = FALSE
)
```

```{r, eval=FALSE, include=FALSE}
library(beepr)
library(checkmate)
library(datadrivencv)
library(dplyr)
library(glue)
library(googlesheets4)
library(here)
library(metathis)
library(pagedown)
library(purrr)
library(rmarkdown)
library(tidyr)
```

```{r, include=FALSE}
source(here::here("R", "printing.R"))
```

```{r metathis, echo = FALSE, message = FALSE, warning = FALSE}
metathis::meta() |>
  metathis::meta_name("github-repo" = "danielvartan/resume-en") |>
  metathis::meta_social(
    title = "Daniel Vartanian's Résumé",
    description = paste(
      "Developed using the R packages {RMarkdown}, {pagedown} and {datadrivencv}."
    ),
    url = "https://danielvartan.github.io/resume-en",
    og_type = "website",
    og_author = "Daniel Vartanian",
    og_locale = "pt_BR"
  )
```

<!-- styles: start -->
<link rel="stylesheet" href="https://cdn.jsdelivr.net/gh/jpswalsh/academicons@1/css/academicons.min.css">
<!-- styles: end -->

<!-- scripts: start -->
<script src="https://kit.fontawesome.com/ddcb976bc4.js" crossorigin="anonymous"></script>
<!-- scripts: end -->

```{r, include = FALSE}
data_location <- paste0(
  "https://docs.google.com/spreadsheets/d/",
  "1enL3ugVvMhzSq2BaYApeuXmpOh0eZUMsMv0yD3YU1_A"
)

# Read all data and initialize a cv printer object
cv <- data_location  |> create_cv_object()
```

# Aside

![Daniel Vartanian](https://avatars.githubusercontent.com/u/29462472?v=4){width=100% style='border-radius: 50%; text-align: center;'}

```{r}
if (isTRUE(params$pdf_mode)) {
  cat(
    "<p style='font-size: 0.7rem; text-align: center;'>",
    "View this résumé online at: ",
    "[danielvartan.github.io/resume-en]",
    "(https://danielvartan.github.io/resume-en)",
    "</p>",
    sep = ""
  )
} else {
  cat(
    "<p style='text-align: center;'>",
    "[<i class = 'fas fa-download'></i> Download this résumé]",
    "(pdf/Daniel%20Vartanian.pdf)",
    "</p>",
    sep = ""
  )
}
```

::: {style="text-align: left; padding-top:10px;"}
<p style="font-size: 0.7rem;">For more information, please refer to my résumé on [LinkedIn](https://www.linkedin.com/in/danielvartan).</p>
:::

::: {style="text-align: left; padding-top:20px;"}
<h2>Contact</h2>

<i class="fa fa-map-marker"></i>  São Paulo, SP, Brazil

<i class="fa-solid fa-phone"></i> [+55 11 95057-9817](https://wa.me/+5511950579817)

<i class="fa-solid fa-envelope"></i> [danvartan@gmail.com](mailto:danvartan@gmail.com)

<i class="fa-brands fa-github"></i> [danielvartan](https://github.com/danielvartan)

<i class="fa-brands fa-linkedin-in"></i> [danielvartan](https://www.linkedin.com/in/danielvartan)

<i class="fa-brands fa-orcid"></i> [0000-0001-7782-759X](https://orcid.org/0000-0001-7782-759X)
:::

::: {style="text-align: left; padding-top:20px;"}
<h2>Programming Languages</h2>

<i class="fab fa-r-project"></i> `R` (Primary)

<i class="fab fa-python"></i> `Python`

<i class="fas fa-database"></i> `SQL`

<i class="fab fa-js"></i> `JavaScript`

<i class="fab fa-html5"></i> `HTML`

<i class="fab fa-css3-alt"></i> `CSS`

<i class="fas fa-code-branch"></i> `Git`
:::

## Disclaimer {#disclaimer}

Developed with R [**pagedown**](https://github.com/rstudio/pagedown) and [**datadrivencv**](https://github.com/nstrayer/datadrivencv) packages.

The code is available on [**GitHub**](https://github.com/danielvartan/resume-en).

Updated on `r format(Sys.Date(), "%B %d, %Y")`.


# Main

## Daniel Vartanian {#title}

<p style="font-size: 1rem;">Complexity Scientist and Data Scientist<p>

## Experience {#experience data-icon=suitcase}

```{r}
cv <- cv |> print_section("experience")
```

## Education {#education data-icon=graduation-cap data-concise=true}

```{r}
cv <- cv |> print_section("education")
```

## Affiliations {#affiliations data-icon=id-badge}

```{r}
cv <- cv |> print_section("memberships")
```

::: {.aside style="top: 10px;"}
<h2>Languages</h2>

<h3>English</h3>

<i class="fa-solid fa-ear-listen"></i> Fluent

<i class="fas fa-book-reader"></i> Fluent

<i class="fa fa-comments-o" aria-hidden="true"></i> Fluent

<i class="fas fa-pencil-alt" aria-hidden="true"></i> Fluent

<h3>Portuguese</h3>

<i class="fa-solid fa-ear-listen"></i> Fluent

<i class="fas fa-book-reader"></i> Fluent

<i class="fa fa-comments-o" aria-hidden="true"></i> Fluent

<i class="fas fa-pencil-alt" aria-hidden="true"></i> Fluent

<h3>Spanish</h3>

<i class="fa-solid fa-ear-listen"></i> Fluent

<i class="fas fa-book-reader"></i> Fluent

<i class="fa fa-comments-o" aria-hidden="true"></i> Intermediate

<i class="fas fa-pencil-alt" aria-hidden="true"></i> Intermediate

<br>

<h2>Skills</h2>

<p style="margin-block-start: 0em;">• Statistical modeling</p>

<p style="margin-block-start: 0em;">• Machine learning</p>

<p style="margin-block-start: 0em;">• Complex systems modeling</p>

<p style="margin-block-start: 0em;">• Agent-based modeling</p>

<p style="margin-block-start: 0em;">• Dynamic systems modeling</p>

<p style="margin-block-start: 0em;">• Complex network modeling</p>

<p style="margin-block-start: 0em;">• Temporal data analysis</p>

<p style="margin-block-start: 0em;">• Spatial data analysis</p>

<p style="margin-block-start: 0em;">• Software development</p>

<p style="margin-block-start: 0em;">• Data engineering</p>

<p style="margin-block-start: 0em;">• Data visualization</p>

<p style="margin-block-start: 0em;">• Dashboards (with R [Shiny](https://shiny.posit.co/))</p>

<p style="margin-block-start: 0em;">• Technical and academic writing</p>

<p style="margin-block-start: 0em;">• Graphic design</p>
:::

\pagebreak

## Projects {#projects data-icon=box-open}

```{r}
cv <- cv |> print_section("software_development")
```

## Main Academic Publications {#publications data-icon=book}

```{r}
cv <- cv |> print_section("academic_articles")
```

::: {.aside style="top: 10px;"}
<h2>Organizations</h2>

<h3>[An Introduction to the R Programming Language](https://danielvartan.github.io/r-course)</h3>

<p>School of Public Health at the University of São Paulo (2025)</p>

<h3>[Agent-Based Modeling Study Group](https://trello.com/b/mzqEtRdm/agent-based-modeling-study-group)</h3>

<p>University of São Paulo (2024)</p>

<h3>[Introductory Course on Actigraphy](https://web.archive.org/web/20211026202625/https://www.sono2021.com.br/evento/sono2021/programacao/gradeatividades)</h3>

<p>XVIII Brazilian Sleep Congress (2021)</p>

<h3>[Sleep at EACH](https://photos.app.goo.gl/spUsAgPNhdnEXQja8)</h3>

<p>Wellness project focused on creating sleep spaces for students, developed at the School of Arts, Sciences, and Humanities, University of São Paulo (2017).</p>

<br>

<h2>Courses</h2>

<h3>[Introduction to Agent-Based Modeling](https://abm.complexityexplorer.org/)</h3>

<p>Santa Fe Institute (2024, Complexity Explorer)</p>

<h3>[São Paulo School of Advanced Science on Ecology of Human Sleep and Biological Rhythms](https://espca.fapesp.br/escola/sao_paulo_school_of_advanced_science_on_ecology_of_human_sleep_and_biological_rhythms/101/)</h3>

<p>University of São Paulo (2022)</p>

<h3>[Circadian Clocks: How Rhythms Structure Life](https://www.coursera.org/learn/circadian-clocks)</h3>

<p>Ludwig-Maximilians-Universität München (2022, Coursera)</p>

<h3>[R Programming](https://www.coursera.org/learn/r-programming)</h3>

<p>Johns Hopkins University (2020, Coursera)</p>

<h3>[Access and Use of Technical-Scientific Information](https://uspdigital.usp.br/apolo/apoObterCurso?cod_curso=860400060&cod_edicao=12001&id_periodo=&id_modalidade=4)</h3>

<p>University of São Paulo (2013)</p>

<h3>Art and Technique of Academic Writing</h3>

<p>University of São Paulo (2013)</p>
:::
